A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-19 manuscript.Rmd
add section on Archiving Docker #82

>>>>

A valid point of criticism is that this workflow introduces a bulk of software solutions and services that may not be available for long.
Superficially it relies on R, RStudio, Pandoc, Git, Make, Docker, Homebrew (OS X only) and Chocolaty (Windows only) as software and on GitHub, DockerHub, MRAN and Ubuntu Package Archive as services.
These many breakpoints can be reduced to one service and one software.
That is because all required software is bundled into the container, whose image can be stored.
Hence, one needs a storage provider which saves the container image and the other files associated with the project.
We already recommend to store all project files redundantly (your computer, on GitHub and zenodo.org).
Building the Docker image from the Dockerfile still requires DockerHub, MRAN, and Ubuntu Package Archive to be online.
We therefore suggest that you include an already build image into the releases.
The Makefile generated by `repro` does include a target to facilitate this.
To write a compressed image to disk use:

```bash
# this should be run in the terminal
make save-docker
```

Unfortunately, this image can only be used when Docker is installed.
To remove any software dependency including Docker from the archived project, one can convert the Docker image to a full system image.
Such system image can subsequently be booted on any personal computer without relying on any software or service and therefore grantees reproducibility for decades to come.
Currently, `repro` does not facilitate this conversion, but we hope to include this feature soon.
